On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-08-04 Manuscript/manuscript.tex
removed addressed comments

\jy{The bib file needs quality control. Practice my writing tips in the
  stat-wriging notes: chapter 2 on latex/bibtex.}

\jy{Go over the reference section to see what need to be changed in the bib source}

@@

\jy{Use double blank lines to separate paragraphs in tex source. Acknowledge if you copy.}
\of{Resolved}

@@

The objective to this paper is to analyze the reaction times at the 2022 World 
Track and Field Championships to check for any abnormalities, and we approach
this in two different ways.  First we model the data, which are
the reaction times of every non-disqualification since the 1999 World 
Championships, using a gamma linear mixed-effects model with two random effects 
one effect for the year and a second effect for the
heat within each year. \jy{do a thorough check to make sure this is updated.}
\of{This should be better now.}
Based on the fitted model, we can then estimate the probability of a reaction 
time being below a certain threshold (e.g., 0.1). 
Second, we compare reaction times for athletes who have competed
at additional competitions to the 2022 World Track and Field Championship.  By
comparing reaction times from the same athlete across multiple competitions we 
are able to determine if the 2022 reaction times differed significantly from 
those of other competitions.
Our investigation into reaction times is important not only because of its
implications for future races, but also because reaction times have
been shown to affect the overall time of the race \citep{delalija2008reaction}.
Thus, faster reaction times lead to faster overall times, which is the goal of
every sprinter who steps onto the track.

@@

\jy{Use the pooled data; present the analysis with 2022 first; then suggest that
  is worth looking at the results without 2022.}

\jy{Write the story up as if you are going to submit. Then I'll review it.}

@@

\jy{condense; could use chatGPT to improve your writing.}

>>>>

@@

@@

The objective to this paper is to analyze the reaction times at the 2022 World 
Track and Field Championships to check for any abnormalities, and we approach
this in two different ways.  First we model the data, which are
the reaction times of every non-disqualification since the 1999 World 
Championships, using a gamma linear mixed-effects model with two random effects 
one effect for the year and a second effect for the
heat within each year.
Based on the fitted model, we can then estimate the probability of a reaction 
time being below a certain threshold (e.g., 0.1). 
Second, we compare reaction times for athletes who have competed
at additional competitions to the 2022 World Track and Field Championship.  By
comparing reaction times from the same athlete across multiple competitions we 
are able to determine if the 2022 reaction times differed significantly from 
those of other competitions.
Our investigation into reaction times is important not only because of its
implications for future races, but also because reaction times have
been shown to affect the overall time of the race \citep{delalija2008reaction}.
Thus, faster reaction times lead to faster overall times, which is the goal of
every sprinter who steps onto the track.

@@

@@
